TacticToe: Learning the Game of Tactics

### 2018-01-29 tactictoe_jv.tex
minro

The first idea is to select tactic-goal pairs and theorems by their distance to 
the conjecture. However, this selection may not be adapted to later stages of 
the proof where goals may have derived significantly from the 
initial conjecture $c$. In order to 
anticipate the production of diverse goals, our prediction during preselection
takes into account dependencies between objects of the same dataset.
The dependence relation is assymetric. Through the relation, each object has 
multiple children and at most one parent.
Once a dependency relation is established, we can calculate a dependency score 
for each object which is the maximum of its similarity score and the similarity 
score of its parent. In the end, the 500 feature vectors in each dataset with 
the highest dependency score are preselected.

@@

\begin{definition} (Coverage)\\ 
Let $\mathfrak{F}$ be a recorded set of feature vectors. We can define the 
coverage $\textit{\mbox{Coverage}}(t)$ of a tactic $t$ by the number of times 
this tactic 
appears in 
$\mathfrak{F}$. Expressing this in a formula, we get:
  \[\textit{\mbox{Coverage}}(t) =_{def} card\ \lbrace (x,g)\ |\ (x,g) \in 
  \mathfrak{F} 
  \wedge x 
  = t
  \rbrace  \]
Intuitively, this notion estimates how general a tactic is by counting the 
number of different goals it is useful for.
\end{definition}

@@

\paragraph{Selection of Abstracted Tactics}
As abstracted tactics do not appear in human proof, we need to find a way to 
predict them so that they can contribute to the \tactictoe proof search.
A straightforward idea is to duplicate each tactic during the proof search by 
creating an abstracted version of the tactic. However, this is computationally 
expensive when the tactic does not instantiate back to its original form, we 
risk doing unnecessary work as both version may have a similar effect.
Therefore, we need to decide beforehand which of the two is better.
In fact, we can re-use the orthogonalization module to do this task for us.
We add $A$ to the competition, initially giving it the coverage of $T$. If $A$ 
wins, it becomes a a label for $g$ is including in the database of tactic 
features and thus can be predicted during a proof search.
After many competitions, the coverage of $A$ may exceed the coverage of $T$. At 
this point, the coverage of $A$ is estimated on its own and not inherited from 
$T$ anymore.

@@

\section{Proof Recording}\label{sec:recording}
\todo{MN + RK: comment technical and hard-to read presentation of the unfolding
mechanism and replace by a high level abstraction. Alternatively, make the 
current version more accessible.}

>>>>

The first idea is to select tactic-goal pairs and theorems by their distance to 
the conjecture. However, this selection may not be adapted to later stages of 
the proof where goals may have derived significantly from the 
initial conjecture $c$. In order to 
anticipate the production of diverse goals, our prediction during preselection
takes into account dependencies between objects of the same dataset.
The dependence relation is assymetric. Through the relation, each object has 
multiple children and at most one parent.
Once a dependency relation is established, we can calculate a dependency score 
for each object which is the maximum of its similarity score and the similarity 
score of its parent. In the end, the 500 entries with highest dependency score 
are preselected in each dataset.

@@

\begin{definition} (Coverage)\\ 
Let $\mathfrak{F}$ be the database of tactics. We can define the 
coverage $\textit{\mbox{Coverage}}(t)$ of a tactic $t$ by the number of times 
this tactic 
appears in 
$\mathfrak{F}$. Expressing this in a formula, we get:
  \[\textit{\mbox{Coverage}}(t) =_{def} card\ \lbrace (x,g)\ |\ (x,g) \in 
  \mathfrak{F} 
  \wedge x 
  = t
  \rbrace  \]
Intuitively, this notion estimates how general a tactic is by counting the 
number of different goals it is useful for.
\end{definition}

@@

\paragraph{Selection of Abstracted Tactics}
As abstracted tactics do not appear in human proof, we need to find a way to 
predict them so that they can contribute to the \tactictoe proof search.
A straightforward idea is to try $A$ before $T$ during the proof search. 
However, this risks doing unnecessary work as they may have a similar effect. 
Therefore, we would like to decide 
beforehand if one is better than the other.
In fact, we can re-use the orthogonalization module to do this task for us.
We add $A$ to the competition, initially giving it the coverage of $T$. If $A$ 
wins, it becomes a a label for $g$ is including in the database of tactic 
features and thus can be predicted during proof search.
After many competitions, the coverage of $A$ may exceed the coverage of $T$. At 
this point, the coverage of $A$ is estimated on its own and not inherited from 
$T$ anymore.

@@

\todoi{remove feature vectors from the paper}
\section{Proof Recording}\label{sec:recording}
